### 2021-11-07 README.Rmd
formatting code

# matrix z
y <- x * 0.5 + rnorm(100, sd = 1)
fit.y <- fitted(lm(y ~ x))
z <- cbind(actual = y,
           fitted = fit.y)

@@

```{r point-columns}
x <- (iris[, c(1,3)])
head(x,5)

y <- (iris[, c(2,4)])
head(y,5)

ggmatplot(x,y)
ggmatplot(x,y, 
          xlab = "Length",
          ylab = "Width",
          legend_label = c("Sepal","Petal"))
```

@@

ggmatplot(x,
  plot_type = "histogram",
  xlab = "Group",
  color = "black",
  fill = c("#F8766D", "#7CAE00", "#00BFC4", "#C77CFF")
) +
  facet_wrap( ~ Group, scales = "free")
```

>>>>

# matrix z
y <- x * 0.5 + rnorm(100, sd = 1)
fit.y <- fitted(lm(y ~ x))
z <- cbind(
  actual = y,
  fitted = fit.y
)

@@

```{r point-columns}
x <- (iris[, c(1, 3)])
head(x, 5)

y <- (iris[, c(2, 4)])
head(y, 5)

ggmatplot(x, y)
ggmatplot(x, y,
  xlab = "Length",
  ylab = "Width",
  legend_label = c("Sepal", "Petal")
)
```

@@

ggmatplot(x,
  plot_type = "histogram",
  xlab = "Group",
  color = "black",
  fill = c("#F8766D", "#7CAE00", "#00BFC4", "#C77CFF")
) +
  facet_wrap(~Group, scales = "free")
```
